DCVtestkit Output Examples

### 2022-10-10 README.qmd
Try to fix the link to the excel and pdf files.

[`dilution_summary.xlsx`] is the output in Excel.

@@

[`dilution_plot.xlsx`] is the output in pdf.

>>>>

[`dilution_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/DCVtestkit_Output/main/dilution_summary.xlsx) is the output in Excel.

@@

[`dilution_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/DCVtestkit_Output/main/dilution_plot.pdf) is the output in pdf.
